% Erik Sutherland's Resume
% Created: 7 Jan 2004
% Last Modified: 17 Jul 2004

\documentclass[11pt,oneside]{article}
\usepackage{geometry}
\usepackage[T1]{fontenc}

\pagestyle{empty}
\geometry{letterpaper,tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in,headheight=0in,headsep=0in,footskip=.3in}

\setlength{\parindent}{0in}
\setlength{\parskip}{0in}
\setlength{\itemsep}{0in}
\setlength{\topsep}{0in}
\setlength{\tabcolsep}{0in}

% Name and contact information
\newcommand{\name}{Erik Sutherland}
\newcommand{\addr}{3255 SE Lake Road, Milwaukie, OR 97222}
\newcommand{\phone}{(503) 970-2779}
\newcommand{\email}{esuther@pdx.edu}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% New commands and environments

% This defines how the name looks
\newcommand{\bigname}[1]{
	\begin{center}\fontfamily{phv}\selectfont\Huge\scshape#1\end{center}
}

% A ressection is a main section (<H1>Section</H1>)
\newenvironment{ressection}[1]{
	\vspace{4pt}
	{\fontfamily{phv}\selectfont\Large#1}
	\begin{itemize}
	\vspace{3pt}
}{
	\end{itemize}
}

% A resitem is a simple list element in a ressection (first level)
\newcommand{\resitem}[1]{
	\vspace{-4pt}
	\item \begin{flushleft} #1 \end{flushleft}
}

% A ressubitem is a simple list element in anything but a ressection (second level)
\newcommand{\ressubitem}[1]{
	\vspace{-1pt}
	\item \begin{flushleft} #1 \end{flushleft}
}

% A resbigitem is a complex list element for stuff like jobs and education:
%  Arg 1: Name of company or university
%  Arg 2: Location
%  Arg 3: Title and/or date range
\newcommand{\resbigitem}[3]{
	\vspace{-5pt}
	\item
	\textbf{#1}---#2 \\
	\textit{#3}
}

% This is a list that comes with a resbigitem
\newenvironment{ressubsec}[3]{
	\resbigitem{#1}{#2}{#3}
	\vspace{-2pt}
	\begin{itemize}
}{
	\end{itemize}
}

% This is a simple sublist
\newenvironment{reslist}[1]{
	\resitem{\textbf{#1}}
	\vspace{-5pt}
	\begin{itemize}
}{
	\end{itemize}
}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Now for the actual document:

\begin{document}

\fontfamily{ppl} \selectfont

% Name with horizontal rule
\bigname{\name}

\vspace{-8pt} \rule{\textwidth}{1pt}

\vspace{-1pt} {\small\itshape \addr \hfill \phone; \email}

\vspace{8 pt}




%%%%%%%%%%%%%%%%%%%%%%%%
\begin{ressection}{Education}

    \begin{ressubsec}{Portland State University}{Portland, OR}{Majoring in Computer Science and in Psychology}
		\ressubitem{GPA: 3.41 (overall), 3.40 (CS major), 3.5 (Psychology major)}
		\ressubitem{Projected Graduation Date: June, 2014}
	\end{ressubsec}

\end{ressection}


%%%%%%%%%%%%%%%%%%%%%%%%
\begin{ressection}{Experience}

    \begin{ressubsec}{Computer Action Team}{Portland, OR}{Systems Administor (claw-1): September 2012 - Present}
		\ressubitem{Manage Linux systems for the College of Engineering at Portland State University.}
		\ressubitem{Use Configuration management and version control extensively.}
		\ressubitem{Develop tools and scripts to improve reliability and functionality of the network.}
		\ressubitem{Assist users with problems and provide documentation.}
        \ressubitem{Lead classes on Linux command line tools.}
	\end{ressubsec}

	\begin{ressubsec}{College of Computer Sciences}{Portland, OR}{Computer Science Tutor: Jan, 2013 - Present}
        \ressubitem{Assist students with into level (161-311) Computer Science questions involving Python, C++, and Java.}
        \ressubitem{Lead workshops for "Intro to Linux", and "Intro to Command line Editors".}
        \ressubitem{Teach essential programming tools, including: Vim, Make, gcc, gdb, valgrind.}
	\end{ressubsec}

\end{ressection}


%%%%%%%%%%%%%%%%%%%%%%%%
\begin{ressection}{Skills}

    \resitem{\textbf{Operating Systems:} Linux (Arch, Red Hat, and Debian/Ubuntu), UNIX (Solaris).}

	\begin{reslist}{Computer Languages:}

        \ressubitem{Proficient in C, Haskell, Markdown, Python, bash.}

        \ressubitem{Familiar with C++, HTML, Java, JavaScript, \LaTeX, Perl, SQL.}

	\end{reslist}

	\begin{reslist}{Tools and Systems:}

        \ressubitem{Proficient in Cabal, GDB, GHC, Git, IRC, Make, Puppet, VIM, ZFS.}

        \ressubitem{Familiar with Apche, BIND, dhcpd, NFS, OpenLDAP, PXE, rsync, Samba.}

	\end{reslist}


\end{ressection}


%%%%%%%%%%%%%%%%%%%%%%%%
\begin{ressection}{Achievements and Activities}

    \resitem{Lead the MCECS Google Glass Dev Team.}

    \resitem{Developed Android app for cyclists to contribute traffic information to the Portland State Portal Database.}

    \resitem{Maintain a presence on Freenode as \textit{MrRacoon}.}

    \resitem{On Github @ \textit{https://github.com/MrRacoon}.}

\end{ressection}


\end{document}
